The function--sheaf dictionary for smooth commutative group schemes over finite fields with finitely generated geometric component group

### 2014-01-24 dictionary.tex
Improvements to the example in the introduction to dictionary.

A simple example will illustrate some of the issues that arise when extending the sheaf--function dictionary to $\QC$-schemes. Consider the etale group scheme $G = \ZZ_{/\Fq}$. Characters of $G(\Fq) = \ZZ$ are neither finite nor bounded, in general. For example, the $\ell$-adic character $\ZZ \to \EEx$ defined by $1 \mapsto 1+ \ell$ is bounded but not finite, while the character $\ZZ \to \EEx$ defined by $1 \mapsto \ell$ is unbounded.  As we show in the paper, $\ell$-adic local systems on $G$ cannot be used to geometrize either of these characters; however, quasicharacter sheaves do the job, handily. We remark that such characters arise when considering unramified quasicharacters of the $p$-adic group $\Qp^\times$  This example informs our choice of the term ``quasicharacter sheaf''. Indeed, in \cite{cunningham-roe:p-adic_tori} we use this paper to geometrize and categorify all quasicharacters of all algebraic tori over all local fields.

>>>>

A simple example will illustrate some of the issues that arise when extending the sheaf--function dictionary to $\QC$-schemes. 
Consider the etale group scheme $G = \ZZ_{/\Fq}$. 
Characters of $G(\Fq) = \ZZ$ are neither finite nor bounded, in general. 
For example, while the $\ell$-adic character $\ZZ \to \EEx$ defined by 
$1 \mapsto -1$ has finite order, the character defined by 
$1 \mapsto 1+ \ell$ does not, although its image is bounded, while the character $\ZZ \to \EEx$ defined by 
$1 \mapsto \ell$ has unbounded image.  
As we show in the paper, $\ell$-adic local systems on $G$ can only be used to geometrize characters of finite order; quasicharacter sheaves, however, provide the geometrization of all characters of $G(\Fq)$.
We remark that characters of finitely generated commutative groups, like $\ZZ$, 
arise when considering unramified quasicharacters of $p$-adic groups, 
such as $\Qp^\times$; in fact, aiming at such characters informs our choice of the term ``quasicharacter sheaf'' here.  Indeed, in \cite{cunningham-roe:p-adic_tori} we use this paper to geometrize and categorify all quasicharacters of all algebraic tori over all local fields.
